\documentclass[a4paper]{letter}

\usepackage[margin=1in]{geometry} % 1 inch all around
\usepackage{url}

\signature{Thomas Junier          \\
Swiss Institute of Bioinformatics \\
\texttt{thomas.junier@sib.swiss}}

\begin{document}
\begin{letter}{
Editors \\
Bioinformatics
}

\address{
Thomas Junier                     \\
Swiss Institute of Bioinformatics \\
Bâtiment Amphipôle                \\
Quartier UNIL-Sorge               \\
CH-1015 Lausanne VD               \\
Switzerland
}
\date{May 22, 2025}
\opening{Dear Editors,}

I am pleased to submit the manuscript titled \emph{Termal: a fast and
    interactive terminal-based viewer for multiple sequence alignments} for
    consideration as an Application Note in Bioinformatics. \texttt{termal} is a
    lightweight, statically-linked terminal-based tool designed for inspecting
    multiple se- quence alignments (MSAs) directly in the console — making it
    particularly suitable for high- performance computing (HPC) environments and
    remote workflows. Unlike existing terminal-based tools, termal combines
    several practical features typically found only in GUI tools, including in-
    teractive navigation, zooming, selectable color maps, consensus and
    conservation visualization, and sequence ordering based on sequence metrics.
    The software is implemented in Rust and is open source (MIT license). It is
    freely available from \url{https://github.com/sib-swiss/termal} (both source and
    binaries for Linux, macOS and Windows). I believe that termal will be a
    useful addition to the toolbox of bioinformaticians who routinely work in
    headless environments or on remote clusters, and who require a fast,
    feature-rich alignment viewer without GUI dependencies. This manuscript has
    not been published elsewhere and is not under consideration by any other
    jour- nal. A preprint version is available on Preprints.org
    \url{https://doi.org/10.20944/preprints202504.1866.v2}. Thank you for considering
    this submission. I look forward to your feedback.

\closing{Sincerely,} 

\end{letter}
\end{document}
